Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-14 doc/main_jfm.tex
small change
fix reference

\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the Janus particle (often a spherical particle with a hydrophobic and a hydrophilic hemisphere) exhibits complex aggregate, clustering and self-assembly into meso- and macroscopic structures that are relevant to a wide range of applications in biology and bioengineering. Whether it is surface chemistry or polarity under an external field, the dynamics of Janus particles is inevitably the combination of long-range hydrodynamics interactions in the presence of short- and intermediate-range particle-particle interactions. 
Recently Fu {\it et al.} illustrated that the hydrophobic interactions between Janus particles in a viscous solvent can be used as a coarse-grained model to capture the mechanics of an elastic bilayer membrane of amphiphilic macromolecules such as lipids \cite{Fu2020_SIAM}. Depending on the total number of Janus particles and their geometry, in a viscous solvent, Janus particles are found to aggregate to form a micelle, a patch of bilayer membrane with open ends, and a self-enclosed bilayer membrane (a vesicle). Using a hybrid continuum model for the interactions between amphiphilic particles in a viscous solvent and formulating it in a boundary integral formulation, Fu {\it et al.} showed that the membrane granularity during fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

In molecular dynamics (MD) simulations, the lipid bilayer membranes are often approximated by an implicit solvent coarse-grained model for lipids (as in the Martini code), where their hydrodynamic interactions are simplified by an implicit solvent. The long-range hydrodynamic interactions and the induced long-range lipid interactions can be captured by combining the Dry Martini with a lattice Boltzmann MD \cite{Brandner2019_SciRep}. Brandner {\it et al.} used this methodology to simulate the hydrodynamics of a nano-sized vesicle under a shear flow, and reproduced the well-know vesicle hydrodynamics  such as tank-treading, tumbling and inter-leaflet slippage (reported from simulations of the Helfrich-type continuum model).

In this work we extend the hybrid continuum model in \cite{Fu2020_SIAM} for the Janus suspension to incorporate the collective hydrodynamics of a Janus suspension under various flows: a linear shear flow, an elongation flow, and a Poiseuille flow. We demonstrate that a vesicle made of Janus particles does behave like a vesicle in these flowing conditions. Furthermore we also show that the hybrid continuum model allows us to investigate the inter-leaflet slippage and rupture of a bilayer membrane due to an imposed flow.

@@

\section{Governing  Equations}
\subsection{\label{mobility}Mobility Problem}
We consider a suspension of $N_b$ particles suspended in a
two-dimensional unbounded domain. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$. Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor). The
process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

@@

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c c c c c }
 $\chi$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
\hline                    
$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
$b$ (pN$\cdot$ns nm$^{-2}$)   & 1.11 & 1.56 & 1.37 & 1.47 & 1.43 & 1.51 & 1.76\\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}

>>>>

\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the Janus particle (often a spherical particle with a hydrophobic and a hydrophilic hemisphere) exhibits complex aggregate, clustering and self-assembly into meso- and macroscopic structures that are relevant to a wide range of applications in biology and bioengineering. Whether it is surface chemistry or polarity under an external field, the dynamics of Janus particles is inevitably the combination of long-range hydrodynamics interactions in the presence of short- and intermediate-range particle-particle interactions. 
Recently Fu {\it et al.} illustrated that the hydrophobic interactions between Janus particles in a viscous solvent can be used as a coarse-grained model to capture the mechanics of an elastic bilayer membrane of amphiphilic macromolecules such as lipids \cite{Fu20}. Depending on the total number of Janus particles and their geometry, in a viscous solvent, Janus particles are found to aggregate to form a micelle, a patch of bilayer membrane with open ends, and a self-enclosed bilayer membrane (a vesicle). Using a hybrid continuum model for the interactions between amphiphilic particles in a viscous solvent and formulating it in a boundary integral formulation, Fu {\it et al.} showed that the membrane granularity during fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

In molecular dynamics (MD) simulations, the lipid bilayer membranes are often approximated by an implicit solvent coarse-grained model for lipids (as in the Martini code), where their hydrodynamic interactions are simplified by an implicit solvent. The long-range hydrodynamic interactions and the induced long-range lipid interactions can be captured by combining the Dry Martini with a lattice Boltzmann MD \cite{Brandner2019}. Brandner {\it et al.} used this methodology to simulate the hydrodynamics of a nano-sized vesicle under a shear flow, and reproduced the well-know vesicle hydrodynamics  such as tank-treading, tumbling and inter-leaflet slippage (reported from simulations of the Helfrich-type continuum model).

In this work we extend the hybrid continuum model in \cite{Fu20} for the Janus suspension to incorporate the collective hydrodynamics of a Janus suspension under various flows: a linear shear flow, an elongation flow, and a Poiseuille flow. We demonstrate that a vesicle made of Janus particles does behave like a vesicle in these flowing conditions. Furthermore we also show that the hybrid continuum model allows us to investigate the inter-leaflet slippage and rupture of a bilayer membrane due to an imposed flow.

@@

\section{Governing  Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider a suspension of $N_b$ particles suspended in a
two-dimensional unbounded domain. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$. Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor). The
process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

@@

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c c c c c }
 $\chi$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
\hline                    
$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
%$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
%$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
$b$ (pN$\cdot$ns nm$^{-2}$)   & 1.11 & 1.56 & 1.37 & 1.47 & 1.43 & 1.51 & 1.76\\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}
